02_DESeq_characterization

### 2019-07-24 analysis/03_DESeq2_characterization.Rmd
now with musical genes tricolor

```{r musicalgenes, cache = T, eval=T}
head(countData)
head(geneinfo)

candidataCounts <- countData
candidataCounts$Name <- row.names(candidataCounts)
candidataCounts <- candidataCounts %>%
  filter(Name %in% c("NP_990797.2", "NP_001138861.1"))
row.names(candidataCounts) <- candidataCounts$Name
candidataCounts$Name <- NULL
candidataCountsT <- t(candidataCounts)
candidataCountsT <- as.data.frame(candidataCountsT)

@@

candidataCountsTcol2 <- candidataCountsTcol %>%
  group_by(sextissue, treatment) %>%
  summarize(GAL = mean(NP_001138861.1, na.rm = TRUE),
            PRL = mean(NP_990797.2, na.rm = TRUE)) %>%
  gather(GAL, PRL, key = "gene", value = "mean")

@@

myplot <- candidataCountsTcol2 %>%
  filter(sextissue %in% c(mygroup)) %>%
ggplot(aes(x = treatment, y = mean)) +
  geom_point(colour = "white") + 
  geom_line(group = 1, color='grey') +
  theme_bw() +
  facet_wrap(~gene, scales = "free", ncol = 1) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  geom_image(aes(image="https://storage.needpix.com/rsynced_images/music-34177_1280.png")) +
  labs(y = "mean gene expression", subtitle = mysusbtitle, x = NULL)

@@

@@

```{r dds, cache = T}
dds.female_hypothalamus <- subsetDESeq(c.colData,  c.countData, "female_hypothalamus")
dds.female_pituitary <- subsetDESeq(c.colData,  c.countData, "female_pituitary" )
dds.female_gonad <- subsetDESeq(c.colData,  c.countData, "female_gonad" )
dds.male_hypothalamus <- subsetDESeq(c.colData,  c.countData, "male_hypothalamus" )
dds.male_pituitary <- subsetDESeq(c.colData,  c.countData, "male_pituitary"  )
dds.male_gondad <- subsetDESeq(c.colData,  c.countData, "male_gonad")
```

>>>>

```{r musicalgenes, cache = T, eval=T}
countData <- c.countData
colData <- c.colData

candidataCounts <- countData
candidataCounts$Name <- row.names(candidataCounts)
candidataCounts <- candidataCounts %>%
  filter(Name %in% c("NP_990797.2", "NP_001138861.1", "NP_001107180.1"))
row.names(candidataCounts) <- candidataCounts$Name
candidataCounts$Name <- NULL
candidataCountsT <- t(candidataCounts)
candidataCountsT <- as.data.frame(candidataCountsT)

@@

candidataCountsTcol2 <- candidataCountsTcol %>%
  group_by(sextissue, treatment) %>%
  summarize(GAL = mean(NP_001138861.1, na.rm = TRUE),
            PRL = mean(NP_990797.2, na.rm = TRUE),
            CALCA = mean(NP_001107180.1, na.rm = TRUE)) %>%
  gather(GAL, PRL, CALCA, key = "gene", value = "mean")

@@

myplot <- candidataCountsTcol2 %>%
  filter(sextissue %in% c(mygroup)) %>%
ggplot(aes(x = treatment, y = mean)) +
  geom_point(colour = "white") + 
  geom_line(group = 1, color='grey') +
  theme_bw() +
  facet_wrap(~gene, scales = "free", ncol = 1) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  geom_image(aes(image="../figures/characterization/note-black-04.png")) +
  labs(y = "mean gene expression", subtitle = mysusbtitle, x = NULL)

@@

musicgeneslines <- function(mygroup, mysusbtitle, mygene, myimage, myylim, myhline){
  myplot <- candidataCountsTcol2 %>%
  filter(sextissue %in% c(mygroup),
         gene == mygene) %>%
    ggplot(aes(x = treatment, y = mean)) +
    geom_point(colour = "white") + 
    theme_minimal() +
    #facet_wrap(~gene,  ncol = 1) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          strip.text = element_text(face = "italic"),
          panel.grid = element_blank(),
          axis.text.y = element_blank()) +
    geom_image(aes(image=myimage)) +
   labs(y = "mean gene expression", subtitle = mysusbtitle, x = NULL) +
    ylim(myylim) + 
    geom_hline(yintercept = myhline, colour="grey")
  return(myplot)
}

musicgenesnolines <- function(mygroup, mysusbtitle, mygene, myimage, myylim, myhline){
  myplot <- candidataCountsTcol2 %>%
  filter(sextissue %in% c(mygroup),
         gene == mygene) %>%
    ggplot(aes(x = treatment, y = mean)) +
    geom_point(colour = "white") + 
    theme_minimal(base_size = 10) +
    #facet_wrap(~gene,  ncol = 1) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          strip.text = element_text(face = "italic"),
          panel.grid = element_blank(),
          axis.text.y = element_blank()) +
    geom_image(aes(image=myimage)) +
   labs(y = "mean gene expression", subtitle = mysusbtitle, x = NULL) +
    ylim(myylim)

  return(myplot)
}

a <- musicgenesnolines("female_hypothalamus", "female hypothalamus", "GAL", "../figures/characterization/note-orange-04.png", c(15,75))
a

b <- musicgenesnolines("male_hypothalamus", "male hypothalamus", "GAL", "../figures/characterization/note-orange-04.png", c(15,75))
b

ab <- plot_grid(a,b) + cowplot::draw_text("GAL", x = 0.925, y = 0.9, size = 8, colour = "#d95f02")
ab

c <- musicgenesnolines("female_hypothalamus", "female hypothalamus", "CALCA", "../figures/characterization/note-teal-04.png", c(0,100))
c

d <- musicgenesnolines("male_hypothalamus", "male hypothalamus", "CALCA", "../figures/characterization/note-teal-04.png", c(0,100))
d

cd <- plot_grid(c,d)  + cowplot::draw_text("CALCA", x = 0.925, y = 0.85, size = 8, colour = "#1b9e77")
cd

e <- musicgenesnolines("female_hypothalamus", "female hypothalamus", "PRL", "../figures/characterization/note-purple-04.png", c(800,3000) )
e

f <- musicgenesnolines("male_hypothalamus", "male hypothalamus", "PRL", "../figures/characterization/note-purple-04.png", c(800,3000))
f

ef <- plot_grid(e,f) + cowplot::draw_text("PRL", x = 0.925, y = 0.8, size = 8, colour = "#7570b3")
ef

pdf("../figures/characterization/musicalgenes-ab.pdf", width = 4, height = 2)
plot(ab)
dev.off()

pdf("../figures/characterization/musicalgenes-cd.pdf", width = 4, height = 2)
plot(cd)
dev.off()

pdf("../figures/characterization/musicalgenes-ef.pdf", width = 4, height = 2)
plot(ef)
dev.off()

@@

```{r dds, cache = T, eval = F}
dds.female_hypothalamus <- subsetDESeq(c.colData,  c.countData, "female_hypothalamus")
dds.female_pituitary <- subsetDESeq(c.colData,  c.countData, "female_pituitary" )
dds.female_gonad <- subsetDESeq(c.colData,  c.countData, "female_gonad" )
dds.male_hypothalamus <- subsetDESeq(c.colData,  c.countData, "male_hypothalamus" )
dds.male_pituitary <- subsetDESeq(c.colData,  c.countData, "male_pituitary"  )
dds.male_gondad <- subsetDESeq(c.colData,  c.countData, "male_gonad")
```
